### 2023-01-17 files/Chapter1/3DModel.tex

 \documentclass[../../main.tex]{subfiles}
\begin{document}
\section{Model problem for a three-dimensional elastic solid} \label{sec:3D_Model}
In this section we introduces the linear theory for a three-dimensional elastic solid. The textbook of Fung \cite{Fung65} with some changes in the notation. \\

 The equation of motion and constitutive equation are given in subsection \ref{ssec:3D_Model:EquationOfMotion}. The dimensionless form of the equation of motion and constitutive equation are derived in subsection \ref{ssec:3D_Model:DimensionlessForm}. Model problems are presented in subsection \ref{ssec:3D_Model:ModelProblems}. The variational form for the vibration problem is given in section \ref{ssec:3D_Model:VariationalForm}. Plane stress is discussed in section \ref{ssec:3D_Model:PlaneStress} \\

@@

In \eqref{eq:3D_Model:EM}, $\rho$ is the density of the elastic body, $T$ is the stress tensor with components $\sigma_{ij}$, $Q$ is an external body force acting on $\Omega$ and $\textrm{div}T$ is the divergence of the tensor $T$ and represented by
\begin{eqnarray}
	\textrm{div}  T & = &
	\begin{bmatrix}
		\partial_1 \sigma_{11} + \partial_2 \sigma_{12} + \partial_3 \sigma_{13}\\
		\partial_1 \sigma_{21} + \partial_2 \sigma_{22} + \partial_3 \sigma_{23}\\
		\partial_1 \sigma_{31} + \partial_2 \sigma_{32} + \partial_3 \sigma_{33}
	\end{bmatrix}. \label{eq:3D_Model:divT}
\end{eqnarray}

Only small vibrations are considered. This means that the local displacements and rotations are small and hence the stress tensor $T$ is symmetric. Let $\textrm{Tr}(T)$ denote the trace of the stress tensor T, that is
\begin{eqnarray}
	\textrm{Tr}(T) & = & \phi_{11} + \phi_{12} + \phi_{13}. \label{eq:stress_tensor_t}
\end{eqnarray}

@@

\subsubsection*{Strain}\label{sssec:3D_Model:Strain}
Infinitesimal strain tensor is defined on $\Omega$ as $\mathcal{E}$ with components
\begin{eqnarray}
	\varepsilon_{ij} = \frac{1}{2}\left( \frac{\partial u_i}{\partial x_j} + \frac{\partial u_j}{\partial x_i} \right). \label{eq:3D_Model:Strain}
\end{eqnarray}

@@

Hooke's Law \eqref{eq:3D_Model:CE} is the constitutive equation for the three-dimensional elastic model used in problems. Conditions for the problems to be well posed, is discussed in Chapter 2.

\subsection{Dimensionless form} \label{ssec:3D_Model:DimensionlessForm}
The dimensionless form of the equation of motion and constitutive equation are derived in this subsection. Suppose $\ell$ represents some notable dimension (eg.the length) of the elastic body and $G$ the shear modulus of elasticity.\\

@@

\subsubsection*{Equations of motion in dimensionless form}\label{sssec:3D_Model:EquationOfMotionDimensionless}
\begin{eqnarray}
	\partial_t^2 u & = & \textrm{div}T + Q \label{eq:3D_Model:EM-D}
\end{eqnarray}
with
\begin{eqnarray}
	\textrm{div}  T & = &
	\begin{bmatrix}
		\partial_1 \sigma_{11} + \partial_2 \sigma_{12} + \partial_3 \sigma_{13}\\
		\partial_1 \sigma_{21} + \partial_2 \sigma_{22} + \partial_3 \sigma_{23}\\
		\partial_1 \sigma_{31} + \partial_2 \sigma_{32} + \partial_3 \sigma_{33}
	\end{bmatrix}.\label{eq:3D_Model:divT-D}
\end{eqnarray}

@@

\begin{equation}
	\begin{aligned}
		\varepsilon_{11} & =  \gamma  ( \sigma_{11} - \nu \sigma_{22}) \qquad \qquad \varepsilon_{33} & = & - \gamma \nu (\sigma_{11} + \sigma_{22})\\
		\varepsilon_{22} & =   \gamma (\sigma_{22} - \nu\sigma_{11}) \qquad \qquad \varepsilon_{12} & = & \  \gamma (1+\nu) \sigma_{12} \label{strain_comp}
	\end{aligned}	
\end{equation}

>>>>

\documentclass[../../main.tex]{subfiles}
\begin{document}
\section{Model problem for a three-dimensional elastic solid} \label{sec:3D_Model}
In this section we introduces the linear theory for a three-dimensional elastic
solid. The textbook of Fung \cite{Fung65} is used with some changes in the
notation. \\

The equation of motion and constitutive equation are given in subsection
\ref{ssec:3D_Model:EquationOfMotion}. The dimensionless form of the equation of
motion and constitutive equation are derived in subsection
\ref{ssec:3D_Model:DimensionlessForm}. Model problems are presented in
subsection \ref{ssec:3D_Model:ModelProblems}. The variational form for the
vibration problem is given in section \ref{ssec:3D_Model:VariationalForm}.
Plane stress is discussed in section \ref{ssec:3D_Model:PlaneStress}

@@

In \eqref{eq:3D_Model:EM}, $\rho$ is the density of the elastic body, $T$ is
the stress tensor with components $\sigma_{ij}$, $Q$ is an external body force
acting on $\Omega$ and $\textrm{div}T$ is the divergence of the tensor $T$ and
represented by
\begin{eqnarray}
	\textrm{div}  T & = &
	\begin{bmatrix}
		\partial_1 \sigma_{11} + \partial_2 \sigma_{12} + \partial_3 \sigma_{13} \\
		\partial_1 \sigma_{21} + \partial_2 \sigma_{22} + \partial_3 \sigma_{23} \\
		\partial_1 \sigma_{31} + \partial_2 \sigma_{32} + \partial_3 \sigma_{33}
	\end{bmatrix}. \label{eq:3D_Model:divT}
\end{eqnarray}

Only small vibrations are considered. This means that the local displacements
and rotations are small. Hence the stress tensor $T$ is symmetric. Let
$\textrm{Tr}(T)$ denote the trace of the stress tensor $T$, that is
\begin{eqnarray}
	\textrm{Tr}(T) & = & \phi_{11} + \phi_{12} + \phi_{13}. \label{eq:stress_tensor_t}
\end{eqnarray}

@@

\subsubsection*{Strain}\label{sssec:3D_Model:Strain}
Infinitesimal strain tensor is defined on $\Omega$ as $\mathcal{E}$, with components
\begin{eqnarray}
	\varepsilon_{ij} = \frac{1}{2}\left( \frac{\partial u_i}{\partial x_j} + \frac{\partial u_j}{\partial x_i} \right). \label{eq:3D_Model:Strain}
\end{eqnarray}

@@

Hooke's Law \eqref{eq:3D_Model:CE} is the constitutive equation for the
three-dimensional elastic model used in problems. Conditions for the problems
to be well posed, are discussed in Chapter 2.

\subsection{Dimensionless form} \label{ssec:3D_Model:DimensionlessForm}
The dimensionless form of the equation of motion and constitutive equation are
derived in this subsection. Suppose $\ell$ represents some notable dimension
(e.g.the length) of the elastic body and $G$ the shear modulus of elasticity.\\

@@

\subsubsection*{Equations of motion in dimensionless form}\label{sssec:3D_Model:EquationOfMotionDimensionless}
\begin{eqnarray}
	\partial_t^2 u & = & \textrm{div}T + Q \label{eq:3D_Model:EM-D}
\end{eqnarray}
with
\begin{eqnarray}
	\textrm{div}  T & = &
	\begin{bmatrix}
		\partial_1 \sigma_{11} + \partial_2 \sigma_{12} + \partial_3 \sigma_{13} \\
		\partial_1 \sigma_{21} + \partial_2 \sigma_{22} + \partial_3 \sigma_{23} \\
		\partial_1 \sigma_{31} + \partial_2 \sigma_{32} + \partial_3 \sigma_{33}
	\end{bmatrix}.\label{eq:3D_Model:divT-D}
\end{eqnarray}

@@

\begin{equation}
	\begin{aligned}
		\varepsilon_{11} & =  \gamma  ( \sigma_{11} - \nu \sigma_{22}) \qquad \qquad \varepsilon_{33} & = & - \gamma \nu (\sigma_{11} + \sigma_{22})          \\
		\varepsilon_{22} & =   \gamma (\sigma_{22} - \nu\sigma_{11}) \qquad \qquad \varepsilon_{12}   & = & \  \gamma (1+\nu) \sigma_{12} \label{strain_comp}
	\end{aligned}
\end{equation}
